---
title: 'Developing Data Product: Week 2 Assignment'
output:
  html_document:
    keep_md: yes
  pdf_document: default
date: "June 18, 2017"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!


## Interactive Map Leaflet

Some New York points of interest: Empire State Building, New York University, One World Trade Center, Metropolitan Museum of Art

```{r}
library(leaflet)
mapNYC = leaflet() %>%
 addTiles() %>%
 addMarkers (lat= 40.7484404, lng= -73.9856554, popup="Empire State Building")%>%
 addMarkers (lat= 40.7291475, lng = -73.9959781, popup="New York University")%>%
 addMarkers (lat= 40.7129947, lng = -74.0131609, popup="One World Trade Center")%>%
 addMarkers (lat= 40.7794366, lng= -73.963244, popup="Metropolitan Museum of Art")

mapNYC
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
